---
title: "Regression"
author: "Avirup Gupta Roy"
date: "6 March 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
EXECUTIVE SUMMARY
Motor Trend,  a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:
	"Is an automatic or manual transmission better for MPG"
	"Quantify the MPG difference between automatic and manual transmissions"
Objective :Using simple linear regression analysis, we determine that there is a signficant difference between the mean MPG for automatic and manual transmission cars. 



```{r}
summary(mtcars)
data(mtcars)
head(mtcars)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am   <- factor(mtcars$am,labels=c("Automatic","Manual"))
summary(mtcars$mpg)
fit <- lm(mpg ~ am, data = mtcars)
summary(fit)
bestfit <- lm(mpg ~., data = mtcars)
summary(bestfit)
anova(fit, bestfit)
print("##The p-value of 0.000285 is small and the CI does not include zero, so we  reject null hypothesis in favor of the alternative hypothesis that there is a significant difference in MPG between the two groups at 95% Confidence Interval.")
print("##Adjusted R squared value is 0.3385 which means that only 33.85% of the regression variance can be explained by our model. We will have to introduce more predictor variables to see if they played a larger role in the model.")
print("p-value = 3.793e-09,hence reject the null hypothesis and state that our Multivariable Model is significantly different than the Simple Linear Regression")
```

## Including Plots


```{r mtcars, echo=FALSE}
mtcars$am   <- factor(mtcars$am,labels=c("Automatic","Manual"))
boxplot(mpg ~ am, data = mtcars, col = (c("yellow","orange")), ylab = "MPG", xlab = "Transmission Type",main="plot 1: boxplot of MPG VS Transmission Type")
bestfit <- lm(mpg ~., data = mtcars)
par(mfrow = c(2,2))
 plot(bestfit)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
